# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
data <- read.csv(unzip("activity.zip"))
summary(data)
```

## What is mean total number of steps taken per day?

### Histogram of steps
```{r}
z<-aggregate(steps~date, data, sum)
histinfo <- hist(z$steps, breaks = 20)
histinfo
```

### Mean of summary of steps

```{r}
mean(z$steps)
```

### Median of summary of steps
```{r}
median(z$steps)
```

## What is the average daily activity pattern?

### Time Series Plot on average steps grouped by interval
```{r}
y<-aggregate(steps~interval, data, mean)
plot.default(x=y$interval, y=y$steps, type="l", xlab="Interval Series", ylab="Mean Steps")
````
### Which interval has the highest steps performed

The highest steps performed are in interval 835 with 206.1698 steps
```{r}
subset(y, y$steps == max(y$steps))
```

## Imputing missing values

1. Identify all n/a entries
2. Generate mean by Interval
3. Replacing n/a entries by mean from second step and combine data completecases with data from replacing frame
    
    
```{r}
  # Step 1
    na <- subset(data, !complete.cases(data))
  # Step 2
    y<-aggregate(steps~interval, data, mean)
  # Step 3
    output <- merge(na, y, by = 'interval', all.y = F)
    output <- output[,c('steps.y','date','interval')]
    names(output)[1] <- c("steps")

    complete <- subset(data, complete.cases(data))
    filledActivity <- rbind (complete, output)

  # Histogramm
    z<-aggregate(steps~date, filledActivity, sum)
    histinfo <- hist(z$steps, breaks = 20)


```
### Mean of summary of steps

```{r}
mean(z$steps)
```

### Median of summary of steps
```{r}
median(z$steps)
```
## Are there differences in activity patterns between weekdays and weekends?

### Identifying weekdays
```{r}
 t <- transform(data, weekend=weekdays(as.Date(data$date)) %in% c("Samstag","Sonntag"))
 index <- c(TRUE, FALSE)
 values <- c("weekend", "weekday")
 t$weekend <- factor(values[match(t$weekend, index)])
 summary(t)
```

### Perform Graph

```{r warning=FALSE}
library(ggplot2)
library(reshape)
y<-aggregate(steps~weekend+interval, t, mean)
ggplot(y, aes(x = interval, y =steps, color=weekend)) + geom_line()

ggplot(data = y, aes(x = interval, y =steps)) + geom_line() + facet_grid(weekend ~ .)
```